\chapter{State of the Art}

\section*{\ac{CI/CD}}
In this chapter, the discussion will focus on the tools and technologies employed in this pipeline. 
Furthermore, other pipeline projects or Capture The Flag (CTF) challenges related to DevOps security will be introduced. 
Before diving into the tools utilized in this pipeline, 
the concept of Continuous Integration (\ac{CI}) and Continuous Deployment (\ac{CD}) will be introduced.

While \ac{CI} and \ac{CD} are distinct acronyms, they are often combined into one term because they are closely related and commonly occur together.
Continuous Integration (\ac{CI}) involves the continuous integration of code, where a set of practices, often automated, 
are implemented to integrate code changes. The term "continuous" in \ac{CI} refers to the ongoing nature of these practices 
rather than the code integration never stopping. \ac{CI} facilitates quicker feedback, 
enabling developers to observe their code in action promptly, making it easier to identify and rectify bugs and errors. 
The adoption of \ac{CI} doesn't necessarily mandate the use of sophisticated tools or pipelines; 
it simply promotes project agility and responsiveness to changes.\\
Continuous Deployment (\ac{CD}) is closely tied to \ac{CI}, as most software, when created, is ultimately exposed 
to users in some form, necessitating deployment. Thus, \ac{CD} complements \ac{CI}, ensuring that software changes 
are efficiently deployed and made available to users.\cite{duvall2007continuous}

The adoption of Continuous Integration and Continuous Deployment (\ac{CI/CD}) 
typically involves the implementation of a pipeline. A pipeline comprises a series of automated 
processes executed in a predefined sequence. It serves to automate tasks such as building, testing, and deploying software.\\
Constructing a pipeline entails utilizing a set of tools to establish an integrated infrastructure.
A pipeline can be as simple as a single script or as complex as a series of scripts orchestrated by a pipeline platform.\\
The tools discussed in this section are specifically those employed in the pipeline for this project. 
Notably, Ngrok, as discussed in Section \ref{sec:ngrok}, is the only tool not utilized in the final pipeline. 
However, its inclusion in this section is warranted as it played a role in addressing 
challenges encountered during the development of the remote pipeline (Section \ref{sec:pipeline_remote}) which not either in use.

\section{Tools}
\label{sec:tools}
\input{chapters/State_of_The_art/tools/docker.tex}

\input{chapters/State_of_The_art/tools/gitea.tex}

\input{chapters/State_of_The_art/tools/drone.tex}

\input{chapters/State_of_The_art/tools/ngrok.tex}

\input{chapters/State_of_The_art/tools/proxy.tex}

\input{chapters/State_of_The_art/tools/registry.tex}

\input{chapters/State_of_The_art/tools/certificate.tex}

\input{chapters/State_of_The_art/ci-cd/other-cicd-tools.tex}

\newpage
