\chapter{Technical Implementation}
\label{sec:technical_implementation}
This section covers the technical part of the pipeline. There will not be much discussion about 
whether one of the pipeline is better than the other or if the implementation is good or not.
Rather I will reflect and discuss that in 
the discussion section \ref{sec:discussion-pipeline}.
Section \ref{sec:pipeline_remote} is about the remote deployment.
Section \ref{sec:pipeline-local} is about the final pipeline product hence 
the local pipeline and it's local deployment.\\\\
The objective of this pipeline is to provide developers with an environment where they can develop and experiment, 
using a setup akin to the production pipeline. They have the flexibility to integrate their own repositories, 
configurations, and other resources into the pipeline to observe its behavior. This enables them to assess and 
refine their development practices based on the pipeline's performance.

Localized pipelines, although less common nowadays, offer a unique advantage. Unlike pipelines hosted on 
cloud-based virtual environments managed by service providers, a localized pipeline resides directly on the developer's machine. 
This grants developers full access to the pipeline's infrastructure, codebase, and configurations. Such accessibility is invaluable 
considering the prevalent use of pipelines 
in modern development workflows, emphasizing the importance of adhering to secure and efficient practices.
For this project the pipeline is constructed with the components that are described in section \ref{sec:tools}.


\input{chapters/Implementation/pipeline-remote.tex}
\newpage

\input{chapters/Implementation/pipeline-local.tex}
\newpage

\input{chapters/Implementation/ctfs.tex}q
