\begin{itemize}
    \item First: Gitea is an open source project and is there subjective to changes at any time. For this project,
    I need to ensure that the end result is the same as when I started the project. 
    To circumvent this, the base image of Gitea is chosen to be version 1.16.5. Now why this version? 
    Based some testing it seems that most of the API admin options are unavailable in version later than 1.19.0. Version between 1.16.5 and 1.19.0
    have changes which impacts the use of admin API options.
    Using the version 1.16.5 Docker image esnure that even though long time developing this project, the base image stay the same and 
    the end result will be same as when i started the project, and when the user pulls the image.
    \item Second: The configuration of Gitea needs to be static. When Gitea is installed, it will prompt the installer of Gitea 
    to specify what that person wants. This information will be stored in a special file called app.ini. This file is 
    used by Gitea to configure itself\ref{fig:gitea_app_ini_remote}. The rest of the app.ini file for this project
    can be found the source code of the project under Gitea/app.ini.
    \item Third: Users needs to be created at initialization, so that when the user start the image via docker-compose. 
    The database is already populated with users, and the user can start using the service right away.
    This is done with python3\cite{python} script which 
    post users to the database via a \ac{RESTAPI}, with admin credentials.
\end{itemize}